Quality Definitions of Qualities

### 2021-10-09 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added reproducibility definitions

>>>>

\begin{defn}
Closeness of the agreement between the results of measurements of the same measurand carried out under changed conditions of measurement \citep{iso2017iec}.
\end{defn}

\begin{defn}
Obtaining consistent results using the same input data, computational steps,  methods, and code, and conditions of analysis \citep{national2019reproducibility}.
\end{defn}

\begin{defn}
Running the same software on the same input data and obtaining the same results \citep{rougier2017sustainable}.
\end{defn}
